Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/results.Rmd
added text about heatmaps.

>>>>

The heatmaps reveal one of two patterns among the nonlocal traits. The first possible pattern is a 
single, mostly blue, square along the diagonal that includes most of the nonlocal traits. The second 
possible pattern involves more than one dark blue square. Chr 5 hotspot is an example of this second 
pattern. Its block-diagonal structure contains off-diagonal blocks that are a mixture of colors.
